Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-02-03 Multiresolution_framework/ltx/manuscript.tex
general edits

B-spline wavelet and scaling functions were formulated independently by \citet{Chui1992b,Chui1992,Unser1993}.  The scaling functions are $m$-th order B-splines and the compact support wavelet functions are a linear combination of scaling functions. B-spline wavelet and scaling functions approach optimal time/frequency localization as the order of the spline increases. In fact, for the cubic B-spline scaling and wavelet functions it is already close to the optimal limit for Gaussian functions\citep{Unser1999}. 
%and they have a better approximation rate than other wavelets with the same number of vanishing moments

@@

In order to analytically calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Lambda_{\theta}$, the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale using the two-scale relation pair defined in equations (\ref{eq:MRA-TwoScalepair1}-\ref{eq:MRA-TwoScalepair2coefs}). For scaling functions this can be done  by usingEq.~\eqref{eq:MRA-TwoScalepair1} recursively, giving

@@

 From Eq.~\eqref{eq:MRA-Wavelettransform} the level of approximation, $j$, can be determined. This way we choose wavelets upto level $j$ which fully describe the spatial frequency contents of the underlying dynamics estimated from the observed field.}

>>>>

B-spline wavelet and scaling functions were formulated independently by \citet{Chui1992b,Chui1992,Unser1993}.  The scaling functions are $m$-th order B-splines and the compact support wavelet functions are a linear combination of scaling functions. B-spline wavelet and scaling functions approach optimal time/frequency localization as the order of the spline increases. In fact, for the cubic B-spline scaling and wavelet functions it is already close to the optimal limit for Gaussian functions \citep{Unser1999}. 
%and they have a better approximation rate than other wavelets with the same number of vanishing moments

@@

In order to analytically calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Gamma$, the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale using the two-scale relation pair defined in equations (\ref{eq:MRA-TwoScalepair1}-\ref{eq:MRA-TwoScalepair2coefs}). For scaling functions this can be done  by usingEq.~\eqref{eq:MRA-TwoScalepair1} recursively, giving

@@

 From Eq.~\eqref{eq:MRA-Wavelettransform} the level of approximation, $j$, can be determined. This way we choose wavelets upto level $j$ which can fully describe the spatial frequency contents of the underlying dynamics estimated from the observed field.}
